Appendix 1: sdmTMB statistical model description

### 2022-01-08 doc/appendix-model.Rmd
Develop timing appendix; edit paper
Fix zeta typo

  "$\\omega_{\\s}$", "\\texttt{omega\\_s}", "Spatial random field at point $\\s$ (knot)",
  "$\\omega_{\\s}^*$", "\\texttt{omega\\_s\\_A}", "Spatial random field at point $\\s$ (interpolated)",
  "$\\zeta_{\\s, t}$", "\\texttt{zeta\\_t}", "Spatially varying coefficient random field at point $\\s$ and time $t$ (knot)",
  "$\\zeta_{\\s, t}^*$", "\\texttt{zeta\\_t\\_A}", "Spatially varying coefficient random field at point $\\s$ and time $t$ (interpolated)",
  "$\\epsilon_{\\s, t}$", "\\texttt{epsilon\\_st}", "Spatiotemporal random field at point $\\s$ and time $t$ (knot)",
  "$\\epsilon_{\\s, t}^*$", "\\texttt{epsilon\\_st\\_A}", "Spatiotemporal random field at point $\\s$ and time $t$ (interpolated)",
  "$\\delta_{\\s,t}$", "\\texttt{b\\_t}", "AR(1) or random walk spatiotemporal deviations (knot)",
  "$\\alpha_g$", "\\texttt{RE}", "IID random intercept deviation for group $g$",

>>>>

  "$\\omega_{\\s}$", "\\texttt{omega\\_s}", "Spatial random field at point $\\s$ (knot)",
  "$\\omega_{\\s}^*$", "\\texttt{omega\\_s\\_A}", "Spatial random field at point $\\s$ (interpolated)",
  "$\\zeta_{\\s}$", "\\texttt{zeta\\_s}", "Spatially varying coefficient random field at point $\\s$ (knot)",
  "$\\zeta_{\\s}^*$", "\\texttt{zeta\\_s\\_A}", "Spatially varying coefficient random field at point $\\s$ (interpolated)",
  "$\\epsilon_{\\s, t}$", "\\texttt{epsilon\\_st}", "Spatiotemporal random field at point $\\s$ and time $t$ (knot)",
  "$\\epsilon_{\\s, t}^*$", "\\texttt{epsilon\\_st\\_A}", "Spatiotemporal random field at point $\\s$ and time $t$ (interpolated)",
  "$\\delta_{\\s,t}$", "\\texttt{b\\_t}", "AR(1) or random walk spatiotemporal deviations (knot)",
  "$\\alpha_g$", "\\texttt{RE}", "IID random intercept deviation for group $g$",
